---
title: "Lab 02 - Plastic waste"
author: "Mason"
date: "03/5/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)


plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)


```

### Exercise 2

```{r plastic-waste-density}

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.17)+
  geom_bar()
```

### Exercise 3

```{r} 

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_violin()
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste_per_cap, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_point()
```

### Exercise 5

> Visualize the relationship between plastic waste per capita and total population as well as plastic waste per capita and coastal population. You will need to make two separate plots. Do either of these pairs of variables appear to be more strongly linearly associated?

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = total_pop, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_point()

ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_point()

plastic_waste %>% select(-c(code,entity,continent))%>%is.na()%>%cor()%>%
corrplot::corrplot()
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```


